Spin canonical divisors of log stacky curves

### 2015-06-24 stacky_write_up/spin_cring.tex
minor citation fixes

Let $\Gamma$ be a {\bf Fuchsian} subgroup, i.e. a discrete subgroup of $PSL_2(\BR)$ acting on the {\bf upper half plane} $\bh$ by fractional linear transformations. We can then consider the orbifold $\Gamma \backslash \bh$ over $\BC$. For example, in the case $\Gamma$ acts freely on $\bh$, $\Gamma \backslash \bh$ is a Riemann Surface over $\BC$. It may well be that $\Gamma \backslash \bh$ is not comapact. Defining $\Delta$ as the divisor of cusps associated to $\Gamma$, we can form a space $\Gamma \backslash \bh^*$ which is a compactification of $\Gamma \backslash \bh,$ with associated {\bf divisor of cusps} $\Delta$. We can now consider the {\bf ring of modular forms} $M(\Gamma) = \oplus_k M_k(\Gamma)$. In this paper, for general $\Gamma$, we sharply bound the degree of the generators and relations for $M(\Gamma).$ This was already answered in \cite[]{vzb:stacky} in the case that $M(\Gamma)$ has $M_{2k}(\Gamma) = 0$ for all $k \in \BZ$, that is, when $\Gamma$ has no odd weight modular forms, and we extend this to all Fuchsian subgroups $\Gamma$.

@@

Folloing Voight and Zureick-Brown, \cite{vzb:stacky}, we examine a much more general setting, generalizing Petri's theorem in many directions.
A divisor $\Delta \in \d X$ is a {\bf log divisor} if $\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct. Let $(\sx,\Delta)$ denote a tame seperably rooted stacky curve over a field $k$ so that $X$ is the coarse space of $\sx$, as defined in \cite{vzb:stacky}[Section 5.2] so that $\di \sx = \div X \bigoplus_{i=1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$. Let $K_\sx = K_X + \sum_{i=1}^{r}\frac{e_i-1}{e_i}P_i.$ In this case, we say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$. Call $\halfcan \in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$, be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx + \Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we say $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$. A {\bf log spin curve} is a triple $(X,\Delta,\halfcan)$ where $(X,\Delta)$ and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$. The central object of study in this paper is the {\bf log spin canonical ring} of $(X,\Delta,L)$ is
\begin{align*}
	R(X,\Delta,L) = \oplus_{n=0}^\infty H^0(X,nL)
\end{align*}
The main theorem of this paper is the following bound on the degree of generators and relations of arbitrary log spin canonical rings:

>>>>

Let $\Gamma$ be a {\bf Fuchsian} subgroup, i.e. a discrete subgroup of $PSL_2(\BR)$ acting on the {\bf upper half plane} $\bh$ by fractional linear transformations. We can then consider the orbifold $\Gamma \backslash \bh$ over $\BC$. For example, in the case $\Gamma$ acts freely on $\bh$, $\Gamma \backslash \bh$ is a Riemann Surface over $\BC$. It may well be that $\Gamma \backslash \bh$ is not comapact. Defining $\Delta$ as the divisor of cusps associated to $\Gamma$, we can form a space $\Gamma \backslash \bh^*$ which is a compactification of $\Gamma \backslash \bh,$ with associated {\bf divisor of cusps} $\Delta$. We can now consider the {\bf ring of modular forms} $M(\Gamma) = \oplus_k M_k(\Gamma)$. In this paper, for general $\Gamma$, we sharply bound the degree of the generators and relations for $M(\Gamma).$ This was already answered in \cite[Chapters 7-9]{vzb:stacky} in the case that $M(\Gamma)$ has $M_{2k}(\Gamma) = 0$ for all $k \in \BZ$, that is, when $\Gamma$ has no odd weight modular forms, and we extend this to all Fuchsian subgroups $\Gamma$.

@@

Folloing Voight and Zureick-Brown, \cite{vzb:stacky}, we examine a much more general setting, generalizing Petri's theorem in many directions.
A divisor $\Delta \in \d X$ is a {\bf log divisor} if $\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct. Let $(\sx,\Delta)$ denote a tame seperably rooted stacky curve over a field $k$ so that $X$ is the coarse space of $\sx$, as defined in \cite[Section 5.2]{vzb:stacky} so that $\di \sx = \div X \bigoplus_{i=1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$. Let $K_\sx = K_X + \sum_{i=1}^{r}\frac{e_i-1}{e_i}P_i.$ In this case, we say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$. Call $\halfcan \in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$, be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx + \Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we say $\sx$ has signature $(g; e_1, \ldots, e_r;\delta)$. A {\bf log spin curve} is a triple $(X,\Delta,\halfcan)$ where $(X,\Delta)$ and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$. The central object of study in this paper is the {\bf log spin canonical ring} of $(X,\Delta,L)$ is
\begin{align*}
	R(X,\Delta,L) = \oplus_{n=0}^\infty H^0(X,nL)
\end{align*}
The main theorem of this paper is the following bound on the degree of generators and relations of arbitrary log spin canonical rings:
